---
title: "Working From the Bara et al. Example"
author: "Will Lowe"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{bara-et-al}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r warning=FALSE, message=FALSE, echo = FALSE}
library(knitr)
knitr::opts_chunk$set(comment = "")
```


```{r, warning=FALSE, message=FALSE}
library(topicdict)
library(quanteda)
```

We'll use the Bara data, and seeds extracted from the dictionary.  
These are all in package `extdata`:
```{r}
doc_folder <- system.file(file.path("extdata", "bara_paras"), package = "topicdict")
seed_file <- system.file(file.path("extdata", "bara_seeds.txt"), package = "topicdict")

## turn this flat file of seeds into a (quanteda dictionary) list as it would be used
seed_list <- Map(function(x){ unlist(strsplit(x, " ")) }, 
                 Filter(function(x){ !grepl(x, pattern = "#") }, # remove comments
                        readLines(seed_file)))

# Original topic names from Bara dictionary
names(seed_list) <- c("advocacy", "legal", "medical", "moral", "procedural", "social")
dict <- dictionary(seed_list)
dict
```

Initialize a model with the default tokenization options, without removing
stopwords or stemming
```{r}
set.seed(12345)

stops <- setdiff(c(stopwords("english"), letters), 
                  c("he", "his", "him", "himself", "she", "hers", "her", "herself"))
model <- topicdict_model(file.path(doc_folder, "*.txt"), dict, stopwords = stops)
```
And run a model.  Takes about 50 iterations to converge.
```{r}
model <- topicdict_train(model, iter = 60)
```

Now let's bundle up the posterior and use the new functions on it
```{r}
post <- topicdict::posterior(model)
top_terms(post, show_seed = TRUE) 
```

But let's look at these in terms of lift (higher proabbility relative to a corpus frequency baseline)
```{r}
top_terms(post, "lift", show_seed = TRUE)
```

We can name topics using their first few words.
```{r}
# suggest some names for topics
tnames <- suggest_topic_names(post, "lift", n = 4)
tnames
```
Note that these would overrides the seed labels, so let's not do that.
```{r}
# post <- set_topic_names(post, tnames)
```
In the future we should probably have these functions make names only for *non*-seeded topics.

Here are the top 2 topics in each document
```
head(top_topics(post))
```
and conversely, the the document that has the most of each topic
```{r}
top_docs(post)
```

