---
title: "Election Platforms 2: Scaling"
author: "Will Lowe"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{election-platforms}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = ""
)

library(topicdict)
library(quanteda)
library(ca)
library(dplyr)
library(ggplot2)
theme_set(theme_minimal())

```

```{r}
dictfile <- system.file("extdata/laver-garry-ajps.ykd", package="topicdict")
# We'll use just the economics sections of this dictionary
dict <- dictionary(file = dictfile)[["Laver and Garry"]][["State in Economy"]]
dict$Neut <- NULL # not interested in this category! Just Pro / Con
# load the corpus
data("corpus_uk_platforms")
```

Preprocess the dictionary to expand the wildcards and filter out low frequency
terms
```{r}
post70s_corpus <- corpus_subset(corpus_uk_platforms, date > 1970)
partyabbrev <- c("Con", "Lib", "Lab", "LD", "LibSDP")
#res_main_parties <- subset(res, main) # for plotting
docvars(post70s_corpus, "main") <- docvars(post70s_corpus, "party") %in% partyabbrev
new_dict <- preprocess_dictionary(dict, post70s_corpus,
                                  min.freq = 5,
                                  remove = stopwords(), 
                                  remove_numbers = TRUE,
                                  remove_punct = TRUE, 
                                  remove_symbols = TRUE,
                                  remove_separators = TRUE, 
                                  remove_hyphens = FALSE)
cbind(old = lapply(dict, length),
      new = lapply(new_dict, length))
```


```{r}
# CA dictionary analysis
dtm_orig <- dfm(post70s_corpus,
                dictionary = new_dict,
                remove = stopwords(), 
                remove_numbers = TRUE,
                remove_punct = TRUE, 
                remove_symbols = TRUE,
                remove_separators = TRUE, 
                remove_hyphens = FALSE)
res <- data.frame(dtm_orig)

# CA with all vocabulary
dd <- dfm(post70s_corpus,
          remove = stopwords(), remove_numbers = TRUE,
          remove_punct = TRUE, remove_symbols = TRUE,
          remove_separators = TRUE, remove_hyphens = FALSE)
dd <- dfm_select(dd, unlist(new_dict))
dd <- dfm_trim(dd, min_termfreq = 5, min_docfreq = 5)
mod <- ca(as.matrix(dd))          # fit a scaling model

# CA with just the dictionary's vocabulary
dd_res <- dfm(post70s_corpus, select = unlist(new_dict))
dd_res <- dfm_select(dd_res, unlist(new_dict))
dd_res <- dfm_trim(dd_res, min_termfreq = 1, min_docfreq = 1)
mod_res <- ca(as.matrix(dd_res))          # fit a scaling model

all_res <- data.frame(docvars(dtm_orig),
                      POS = (res$Con - res$Pro) / (res$Con + res$Pro),
                      logitPOS = log(res$Con) - log(res$Pro),
                      ca_dim1 = -mod$rowcoord[,1],
                      ca_dim2 =  mod$rowcoord[,2],
                      ca_dim1_res = mod_res$rowcoord[,1],
                      ca_dim2_res = mod_res$rowcoord[,2])

meta <- docvars(post70s_corpus) # use this when needed
all_res <- data.frame(meta, all_res)
```
One substantively sensible way to plot this 'gold standard' is as time series of
the main parties
```{r, fig.width=15, fig.height=10}
all_res %>% 
  filter(main) %>%
  ggplot(aes(date, ca_dim1_res, color = party)) +
  geom_line() +
  geom_point() +
  geom_vline(xintercept = c(1992, 1997), alpha = 0.1, size = 5 ) +
  scale_color_manual(values = c("blue", "red", "orange", "orange", "orange")) +
  coord_flip()
```

```{r}
left <- -mod$colcoord[intersect(rownames(mod$colcoord), new_dict$Pro), 1]
right <- -mod$colcoord[intersect(rownames(mod$colcoord), new_dict$Con), 1]

df <- dfm(post70s_corpus,
          remove = stopwords(), remove_numbers = TRUE,
          remove_punct = TRUE, remove_symbols = TRUE,
          remove_separators = TRUE, remove_hyphens = FALSE)
freqs <- colSums(df)
freq_left <- freqs[names(left)]
freq_right <- freqs[names(right)]

w_left <-  freq_left / sum(freq_left)
w_right <-  freq_right / sum(freq_right)

mean_left <- weighted.mean(left, w_left)  
mean_right <- weighted.mean(right, w_right)

sd_left <- sqrt(weighted.mean((left - mean_left)^2, w_left))
sd_right <- sqrt(weighted.mean((right - mean_right)^2, w_right))

se_left <- sd_left * sum(w_left^2)
se_right <- sd_right * sum(w_right^2)

cat("CA scores for dictionary words:\n",
    "Mean Left: ", round(mean_left, 3), 
    "SE: ", round(se_left, 3), "(corpus freq weighted)\n",
    "Mean Right: ", round(mean_right, 3), 
    "SE: ", round(se_right, 3), "(corpus freq weighted)\n")

#data.frame(side = c(rep("left", length(left)), 
#                    rep("right", length(right))),
#           score = c(left, right)) %>%
#  ggplot(aes(x = score, fill = side)) +
#    geom_density(alpha = 0.5, col = NA)
 
```

Now restricted to just the dictionary's vocabulary

```{r}
left <- mod_res$colcoord[intersect(rownames(mod_res$colcoord),
                                   new_dict$Pro), 1]
right <- mod_res$colcoord[intersect(rownames(mod_res$colcoord), 
                                    new_dict$Con), 1]

df <- dfm(post70s_corpus,
          remove = stopwords(), remove_numbers = TRUE,
          remove_punct = TRUE, remove_symbols = TRUE,
          remove_separators = TRUE, remove_hyphens = FALSE)
freqs <- colSums(df)
freq_left <- freqs[names(left)]
freq_right <- freqs[names(right)]

w_left <-  freq_left / sum(freq_left)
w_right <-  freq_right / sum(freq_right)

mean_left <- weighted.mean(left, w_left)  
mean_right <- weighted.mean(right, w_right)

sd_left <- sqrt(weighted.mean((left - mean_left)^2, w_left))
sd_right <- sqrt(weighted.mean((right - mean_right)^2, w_right))

se_left <- sd_left * sum(w_left^2)
se_right <- sd_right * sum(w_right^2)

cat("CA scores for dictionary words:\n",
    "Mean Left: ", round(mean_left, 3), 
    "SE: ", round(se_left, 3), "(corpus freq weighted)\n",
    "Mean Right: ", round(mean_right, 3), 
    "SE: ", round(se_right, 3), "(corpus freq weighted)\n")

#data.frame(side = c(rep("left", length(left)), 
#                    rep("right", length(right))),
#           score = c(left, right)) %>%
#  ggplot(aes(x = score, fill = side)) +
#    geom_density(alpha = 0.5, col = NA)
 
```


We can generate 'wordscore' type quantities by looking at the logit of the word
generation probabilities from the topic model and comparing them to the scaling
scores:

```{r}
set.seed(1234)
mod5 <- topicdict_model(post70s_corpus, dict = new_dict,
                stopwords = stopwords(), remove_numbers = TRUE,
                remove_punct = TRUE, remove_symbols = TRUE,
                remove_separators = TRUE, remove_hyphens = FALSE,
                extra_k = 5)
mod5 <- topicdict_train(mod5, 340)
post <- posterior(mod5)

on_topic_left <- post$beta["Pro", new_dict$Pro]
not_pro <- setdiff(rownames(post$beta), "Pro")
off_topic_left <- colSums(post$beta[not_pro, new_dict$Pro])
diff_left <- off_topic_left - on_topic_left # -ve more 'correct'

on_topic_right <- (post$beta["Con", new_dict$Con])
not_con <- setdiff(rownames(post$beta), "Con")
off_topic_right <- colSums(post$beta[not_con, new_dict$Con])
diff_right <- on_topic_right - off_topic_right # +ve more 'correct'

sorted_diff_right <- sort(diff_right)
#plot(right[names(diff_right)], sorted_diff_right)
ptab <- prop.table(table(td = ifelse(diff_right >= 0, ">=0 (correct)", "<0"), 
                         ws = ifelse(right >= 0, ">=0", "<0")))
addmargins(round(ptab, 2))

ptab <- prop.table(table(td = ifelse(diff_left < 0, "<0 (correct)", ">=0"),
                         ws = ifelse(left < 0, "<0", ">=0")))
addmargins(round(ptab, 2))

```

Dictionary right that scaling model thinks are left
```{r}
names(diff_right[diff_right >= 0 & right < 0])
```

Dictionary left that scaling model thinks are right
```{r}
names(diff_left[diff_left < 0 & left > 0])
```


Turns out the positions are pretty close from manual dictionary and 
scores from the logit scoring the topicdict output
```{r}
cmat <- data.frame(pos_manual = all_res$logitPOS, 
                   pos_ca = all_res$ca_dim1,
                   pos_ca_res = all_res$ca_dim1_res,
                   pos_topicdict = log(post$theta[,2] / post$theta[,1]))

# overall postion correlations
cor(cmat)

# scaling model is much better fit for the main parties (obvs)
# but topicdict still good
cor(cmat[all_res$main,])

# and
cor(cmat[!all_res$main,])
```

```{r}
dd <- data.frame(pos_manual = (all_res$logitPOS), 
                 pos_topicdict = (log(post$theta[,2] / post$theta[,1])),
                 main = ifelse(all_res$main, "main", "other"))
ggplot(dd, aes(x = pos_manual, y = pos_topicdict, color = main)) +
  geom_point() + 
  geom_smooth(method = "lm", se = FALSE) +
  xlab("Logit score from dictionary") + 
  ylab("Logit score from topicdict")
```




