---
title: "Simulation Study"
author: "Shusei Eshima and Tomoya Sasaki"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
toc: true
vignette: >
  %\VignetteIndexEntry{SimulationStudy}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Set Chunk Options

```{r warning=FALSE, message=FALSE}
library(knitr)
knitr::opts_chunk$set(comment = "")
```

# Preparation

## Prepare Packages

```{r, message=FALSE}
library(topicdict)
library(tidyverse)
library(quanteda)
num_iteration <- 10
```

## Define a function
Run simulation code:
```{r, warning=FALSE, message=FALSE}
show_true_seed <- function(data_folder_name, seed_file_name = "SeedWords.csv"){
	seed_file <- paste0(data_folder, data_folder_name, "/", seed_file_name)
	true_seed <- invisible(readr::read_csv(seed_file))
	message("Row: Topic / Column: Seed word")
	print(true_seed)
}


topicdict_simulation_run <- function(data_folder_name, iter, extra_k, 
																		 seed_file_name="SeedWords.csv", seed_list = NULL,
																		 cull_seed=NULL){

	# cull_seed: Which row (=topic) and column (=number of seed) to use

	set.seed(225)

	folder <- paste0(data_folder, data_folder_name, "/W")
	docs <- list.files(folder, pattern = "*.txt", full.names = TRUE)

	seed_file <- paste0(data_folder, data_folder_name, "/", seed_file_name)

	seeddata <- invisible(readr::read_csv(seed_file))

	if(!is.null(cull_seed)){
		seeddata <- seeddata[1:cull_seed[1], 1:cull_seed[2]]
	}

	if(is.null(seed_list)){
		seed_list <- as.list( apply(seeddata, 1, function(x){return(paste0(x, collapse=" "))}) )
	}
	names(seed_list) <- 1:length(seed_list)
	dict <- quanteda::dictionary(seed_list)

	model <- topicdict_model(docs,
							 dict = dict, extra_k = extra_k,
							 remove_numbers = FALSE, # For simulation, make it false
							 remove_punct = TRUE,
							 remove_symbols = TRUE,
							 remove_separators = TRUE)

	res <- topicdict_train(model, iter = iter)
	
	return(res)
}
```

Visualization:
```{r, warning=FALSE, message=FALSE}
diagnosis_topic_recovery <- function(post, n=25){
	topwords <- top_terms(post, n=n)
	topwords <- data.frame(topwords)
	colnames(topwords) <- paste0("EstTopic", 1:ncol(topwords))

	topwords <- tidyr::gather(topwords, key=EstTopic, value=Word)

	topwords %>%
		mutate(RawWord = Word) %>%
		separate(Word,
				into=c("TrueTopic", "word_id"),
				sep="r|s") %>%
		mutate(TrueTopic = paste0("True", as.character(TrueTopic))) %>%
		group_by(EstTopic, TrueTopic) %>%
		summarise(counts = n()) %>%
		ungroup() %>%
		group_by(EstTopic) %>% 
		mutate(topicsum = sum(counts)) %>%
		ungroup() %>%
		mutate(Proportion = counts / topicsum * 100,
					 Estimated = EstTopic) -> res

		num <- length(unique(res$Estimated))
		truenum <- length(unique(res$TrueTopic))

		title <- paste0("Top ", as.character(n), " words")

		g <- ggplot(res, aes(x=Estimated, y=Proportion, fill=TrueTopic)) +
					geom_bar(stat="identity") +
					scale_x_discrete(limits = rev(paste0("EstTopic", 1:num))) +
					coord_flip() +
					scale_fill_hue(name = "True Topics", breaks=paste0("True", 1:truenum)) + 
					xlab("Estimated Topics") + ylab("Proportion (%)") + theme_bw(base_size=16) +
					ggtitle(title) +
					theme(plot.title = element_text(hjust = 0.5))

		return(g)
}
```

# Simulation

## Simulation 1 (numtopic = 15, flat alpha)
```{r, warning=FALSE, message=FALSE, fig.width=5, fig.height=5}
data_folder <- tempfile()
create_sim_data(saveDir=paste0(data_folder, "Sim1"), D=1000, K=15, TotalV=3000, alpha=0.1, beta_r=0.1, beta_s=0.1, p=rep(0.2, 15), lambda=200, seeds_len=5)
```

### Split True Seed, number of topics is truth
```{r, warning=FALSE, message=FALSE}
show_true_seed("Sim1")
seed_list <- list(c("1S3 1S140"),
								 c("1S42 1S154"),
								 c("3S42 3S75 3S83"),
								 c("4S11 4S200 4S97"))

res <- topicdict_simulation_run("Sim1", seed_list=seed_list, iter=num_iteration, extra_k=11)
post <- posterior(res)
diagnosis_alpha(post, start=5, show_topic=c(1,2,3,4), true_vec=rep(0.1, 15))
```

```{r, warning=FALSE, message=FALSE, fig.width=6, fig.height=4}
diagnosis_model_fit(post, start=2)
```

```{r, warning=FALSE, message=FALSE, fig.width=7, fig.height=8}
diagnosis_topic_recovery(post)
```

### Split True Seed, underestimated number of topics 
```{r, warning=FALSE, message=FALSE}
show_true_seed("Sim1")
seed_list <- list(c("1S3 1S140"),
								 c("1S42 1S154"),
								 c("3S42 3S75 3S83"),
								 c("4S11 4S200 4S97"))

res <- topicdict_simulation_run("Sim1", seed_list=seed_list, iter=num_iteration, extra_k=8)
post <- posterior(res)
diagnosis_alpha(post, start=5, show_topic=c(1,2,3,4), true_vec=rep(0.1, 15))
```

```{r, warning=FALSE, message=FALSE, fig.width=6, fig.height=4}
diagnosis_model_fit(post, start=2)
```

```{r, warning=FALSE, message=FALSE, fig.width=7, fig.height=8}
diagnosis_topic_recovery(post)
```

### Split True Seed, overestimated number of topics 
```{r, warning=FALSE, message=FALSE}
show_true_seed("Sim1")
seed_list <- list(c("1S3 1S140"),
								 c("1S42 1S154"),
								 c("3S42 3S75 3S83"),
								 c("4S11 4S200 4S97"))

res <- topicdict_simulation_run("Sim1", seed_list=seed_list, iter=num_iteration, extra_k=15)
post <- posterior(res)
diagnosis_alpha(post, start=5, show_topic=c(1,2,3,4), true_vec=rep(0.1, 15))
```

```{r, warning=FALSE, message=FALSE, fig.width=6, fig.height=4}
diagnosis_model_fit(post, start=2)
```

```{r, warning=FALSE, message=FALSE, fig.width=7, fig.height=8}
diagnosis_topic_recovery(post)
```

### Merge True Seed, number of topics is truth
```{r, warning=FALSE, message=FALSE}
show_true_seed("Sim1")
seed_list <- list(c("1S3 1S140 1S42"),
								 c("2S190 2S163 3S42 3S75"),
								 c("4S11 4S200 6S200"))

res <- topicdict_simulation_run("Sim1", seed_list=seed_list, iter=num_iteration, extra_k=12)
post <- posterior(res)
diagnosis_alpha(post, start=5, show_topic=c(1,2,3,4), true_vec=rep(0.1, 15))
```

```{r, warning=FALSE, message=FALSE, fig.width=6, fig.height=4}
diagnosis_model_fit(post, start=2)
```

```{r, warning=FALSE, message=FALSE, fig.width=7, fig.height=8}
diagnosis_topic_recovery(post)
```



### Merge True Seed, underestimated number of topics 
```{r, warning=FALSE, message=FALSE}
show_true_seed("Sim1")
seed_list <- list(c("1S3 1S140 1S42"),
								 c("2S190 2S163 3S42 3S75"),
								 c("4S11 4S200 6S200"))

res <- topicdict_simulation_run("Sim1", seed_list=seed_list, iter=num_iteration, extra_k=8)
post <- posterior(res)
diagnosis_alpha(post, start=5, show_topic=c(1,2,3,4), true_vec=rep(0.1, 15))
```

```{r, warning=FALSE, message=FALSE, fig.width=6, fig.height=4}
diagnosis_model_fit(post, start=2)
```

```{r, warning=FALSE, message=FALSE, fig.width=7, fig.height=8}
diagnosis_topic_recovery(post)
```

### Merge True Seed, overestimated number of topics 
```{r, warning=FALSE, message=FALSE}
show_true_seed("Sim1")
seed_list <- list(c("1S3 1S140 1S42"),
								 c("2S190 2S163 3S42 3S75"),
								 c("4S11 4S200 6S200"))

res <- topicdict_simulation_run("Sim1", seed_list=seed_list, iter=num_iteration, extra_k=15)
post <- posterior(res)
diagnosis_alpha(post, start=5, show_topic=c(1,2,3,4), true_vec=rep(0.1, 15))
```

```{r, warning=FALSE, message=FALSE, fig.width=6, fig.height=4}
diagnosis_model_fit(post, start=2)
```

```{r, warning=FALSE, message=FALSE, fig.width=7, fig.height=8}
diagnosis_topic_recovery(post)
```

## Simulation 2 (numtopic = 10, uneven alpha)
```{r, warning=FALSE, message=FALSE, fig.width=7, fig.height=6}
data_folder <- tempfile()
alpha_vec <- c(0.1, 0.2, 0.3, 0.1, 0.2, 0.3, 0.1, 0.2, 0.3, 0.1)
create_sim_data(saveDir=paste0(data_folder, "Sim2"), D=1000, K=10, TotalV=3000, alpha=alpha_vec, beta_r=0.1, beta_s=0.1, p=rep(0.2, 10), lambda=200, seeds_len=5)
```

### Split True Seed, number of topics is truth
```{r, warning=FALSE, message=FALSE, fig.width=7, fig.height=6}
show_true_seed("Sim2")
seed_list <- list(c("1S4 1S210"),
								 c("1S63 1S232"),
								 c("3S63 3S113 3S118"),
								 c("4S16 4S17 4S146"))
res <- topicdict_simulation_run("Sim2", iter=num_iteration, extra_k=6)
post <- posterior(res)
diagnosis_alpha(post, start=5, show_topic=c(1,2,3), true_vec=alpha_vec)
```

```{r, warning=FALSE, message=FALSE, fig.width=6, fig.height=4}
diagnosis_model_fit(post, start=2)
```

```{r, warning=FALSE, message=FALSE, fig.width=7, fig.height=8}
diagnosis_topic_recovery(post)
```

### Merge True Seed, number of topics is truth
```{r, warning=FALSE, message=FALSE, fig.width=7, fig.height=6}
show_true_seed("Sim2")
seed_list <- list(c("1S4 1S210"),
								 c("2S284 2S245 5S184 5S192"),
								 c("3S63 3S113 3S118"),
								 c("4S16 4S17 4S146"))
res <- topicdict_simulation_run("Sim2", iter=num_iteration, extra_k=6)
post <- posterior(res)
diagnosis_alpha(post, start=5, show_topic=c(1,2,3), true_vec=alpha_vec)
```

```{r, warning=FALSE, message=FALSE, fig.width=6, fig.height=4}
diagnosis_model_fit(post, start=2)
```

```{r, warning=FALSE, message=FALSE, fig.width=7, fig.height=8}
diagnosis_topic_recovery(post)
```


## Simulation 3 (numtopic = 15, flat alpha, uneven p)
```{r, warning=FALSE, message=FALSE, fig.width=5, fig.height=5}
data_folder <- tempfile()
p_vec <- c(0.01, 0.03, 0.05, 0.1, rep(0.2, 11))
create_sim_data(saveDir=paste0(data_folder, "Sim3"), D=1000, K=15, TotalV=3000, alpha=0.1, beta_r=0.1, beta_s=0.1, p=p_vec, lambda=200, seeds_len=5)
```

### Number of Topic is the same as the truth, use part of seed (4 topic)
```{r, warning=FALSE, message=FALSE, fig.width=7, fig.height=6}
show_true_seed("Sim3")
seed_list <- list(c("1S4 1S210"),
								 c("2S284 2S245 5S184 5S192"),
								 c("3S63 3S113 3S118"),
								 c("4S16 4S17 4S146"))
res <- topicdict_simulation_run("Sim1", iter=num_iteration, extra_k=11, cull_seed=c(4, 3))
post <- posterior(res)
diagnosis_alpha(post, start=5, show_topic=c(1,2,3,4), true_vec=rep(0.1, 15))
```

```{r, warning=FALSE, message=FALSE, fig.width=6, fig.height=4}
diagnosis_model_fit(post, start=2)
```

```{r, warning=FALSE, message=FALSE, fig.width=7, fig.height=8}
diagnosis_topic_recovery(post)
```


### Topic number misspecification (fewer), use part of seed (4 topic)
```{r, warning=FALSE, message=FALSE, fig.width=7, fig.height=6}
res <- topicdict_simulation_run("Sim1", iter=num_iteration, extra_k=5, cull_seed=c(4, 3))
post <- posterior(res)
diagnosis_alpha(post, start=5, show_topic=c(1,2,3,4), true_vec=rep(0.1, 9))
```

```{r, warning=FALSE, message=FALSE, fig.width=6, fig.height=4}
diagnosis_model_fit(post, start=2)
```

```{r, warning=FALSE, message=FALSE, fig.width=7, fig.height=8}
diagnosis_topic_recovery(post)
```


### Topic number misspecification (more), use part of seed (4 topic)
```{r, warning=FALSE, message=FALSE, fig.width=7, fig.height=6}
res <- topicdict_simulation_run("Sim1", iter=num_iteration, extra_k=15, cull_seed=c(4, 3))
post <- posterior(res)
diagnosis_alpha(post, start=5, show_topic=c(1,2,3,4), true_vec=rep(0.1, 15))
```

```{r, warning=FALSE, message=FALSE, fig.width=6, fig.height=4}
diagnosis_model_fit(post, start=2)
```

```{r, warning=FALSE, message=FALSE, fig.width=7, fig.height=8}
diagnosis_topic_recovery(post)
```
