---
title: "keyATM Base"
output: 
  html_document:
    toc: true
---

```{r setup II, include=FALSE, eval=TRUE}
knitr::opts_chunk$set(eval = T, echo = TRUE)
```

## Preparing documents and keywords
Please read [Preparation](Preparation.html) for the reading of documents and creating a list of keywords. 
We use the US Presidential inaugural address data we prapared ([documents](Preparation.html#reading-documents-into-keyatm) and [keywords](Preparation.html#preparing-keywords)).

## Fitting the model

We pass the output of the `keyATM_read` function and 
keywords to the `keyATM` function.
Additionally, we need to specify the number of topics
without keywords (the `no_keyword_topics` argument) and model.
Since this example does not use covariates or time stamps, `base` is the appropriate model.
To guarantee the replicability, we recommend to set the random seed
in the `option` argument (see [here](Options.html)
for other options). The default number of iterations is 1500.

```{r, warning=FALSE, message=FALSE, fig.align='center', results="hide"}
out <- keyATM(docs              = keyATM_docs,    # text input
              no_keyword_topics = 5,              # number of topics without keywords
              keywords          = keywords, # keywords
              model             = "base",         # select the model
              options           = list(seed = 250)
             )
```
The default number of iterations is `1500`. Please check [this page](Options.html) for available options.


## Saving the model

Once you fit the model, you can save the model with `save()` for replication.
```{r, eval=F, warning=FALSE, message=FALSE, fig.align='center'}
save(out, file = "SAVENAME.rds")
```

To load the model, you can use `readRDS()` function.
```{r, eval=F, warning=FALSE, message=FALSE, fig.align='center'}
out <- readRDS(file = "SAVENAME.rds")
```

## Interpreting results
There are two main quantities of interest in topic models. 
First, topic-word distribution represents the relative frequency of words for each topics, characterizing the topic content. 
Second, document-topic distribution represents the proportions of topics for each document, reflecting the main themes of the document and often called topic prevalence.

Since typical corpus contains several thousands of unique terms, we usually scrutinize ten to fifteen words that have high probabilities in a given topic, which is called top words of a topic. 
The `top_words` function returns a table of top words for each of estimated topics.
Keywords assigned to a keyword topic are suffixed with a check mark.
Keywords from another keyword topic are labeled with the topic id of that category.
In the table below, "law", "laws", and "executive" are keywords of the 
*Government* topic, while ``peace'' appears in top words of the *Other_3* topic,
it is a keyword of the *peace* topic. 

```{r, eval = FALSE, warning=FALSE, message=FALSE, fig.align='center'}
top_words(out)

#     1_Government   2_Congress     3_Peace   4_Constitution 5_ForeignAffairs
# 1        law [✓]        great   world [✓]           states           public
# 2       laws [✓]      justice         new       government            union
# 3          state congress [✓] freedom [✓] constitution [✓]          war [✓]
# 4  executive [✓]       united     america            power          nations
# 5         policy      service         let         citizens      foreign [✓]
# 6          whole    party [✓]   peace [✓]       rights [✓]       principles
# 7       american        force        life             duty           duties
# 8        however       office        time        interests             good
# 9         spirit        means        work           united             just
# 10          full   prosperity    american           powers         interest
#      Other_1        Other_2   Other_3  Other_4    Other_5
# 1      years       national   country   nation     people
# 2     fellow      political peace [3]      men government
# 3    purpose administration      time     hope      every
# 4  president         system   support    first        one
# 5     spirit     confidence    secure progress        now
# 6        day        federal important      man       made
# 7        yet        liberty     since    power      right
# 8   strength          whose   respect  country       well
# 9       come           take    future   change       many
# 10   believe          given resources     find       much
```

To explore documents that are highly associated with each topic, the `top_docs`
function returns a table of document indexes in which a topic has high proportion.
The table below indicates, for example, that the ninth document in the corpus has the 
highest proportion of the *Government* topic among all other documents. 

```{r, eval = FALSE, warning=FALSE, message=FALSE, fig.align='center'}
top_docs(out)
#    1_Government 2_Congress 3_Peace 4_Constitution 5_ForeignAffairs
# 1             9         31      52              2                5
# 2            14         35      47             15               10
# 3             8         34      53             12               11
# 4            26         32      58             11                6
# 5            16         36      46             14                3
# 6            13         29      40             18               15
# 7            19         28      57             19                7
# 8            12         41      51              9                8
# 9            28         33      50             23               20
# 10           36         30      54             17               16
#    Other_1 Other_2 Other_3 Other_4 Other_5
# 1       46       1      28      45      19
# 2       47      31       8      44      21
# 3       54      27       6      38       2
# 4       48      11      31      58       4
# 5       53      36      35      51      20
# 6       49      33      22      30       1
# 7       50      23      23      55      53
# 8       56      17      10      39      32
# 9       57      37       9      46      45
# 10      43      25      16      52      58
```

Researchers may want to obtain the entire document-topic distribution and
topic-word distribution. The output of the `keyATM` function contains both
quantities.

```{r, eval = FALSE, warning=FALSE, message=FALSE, fig.align='center'}
out$theta  # Document-topic distribution
out$phi    # Topic-word distribution
```

The **keyATM** provides other functions to diagnose and explore the fitted model.
First, it is important to check the model fitting. 
If the model is working as expected, we would observe an increase trend for 
the log-likelihood and an decrease trend for the perplexity.
Also the fluctuation of these values get smaller as iteration increases. 
The `plot_modelfit` function visualizes
the within sample log-likelihood and perplexity and the created figure
can be saved with the `save_fig` function. 
<!-- The figure shows that the increase of log-likelihood and the decrease of perplexity.  -->
<!-- Also, the lines get flatter as iteration increases. These results indicate an example of  -->
<!-- the good model fit. -->

```{r, eval = FALSE, warning = FALSE, message = FALSE}
fig_modelfit <- plot_modelfit(out)
save_fig(fig_modelfit, "figures/base_modelfit.pdf", width = 7, height = 5)
```

Furthermore, the **keyATM** can visualize $\balpha$, the prior for the document-topic distribution, and $\bpi$, the probability that each topic uses keyword topic-word distribution.
Values of these parameters should also stabilize over time.

```{r, eval = FALSE, warning = FALSE, message = FALSE}
plot_alpha(out)
plot_pi(out)
```


