---
title: "keyATM Dynamic"
output: 
  html_document:
    toc: true
---

```{r setup II, include=FALSE, eval=TRUE}
knitr::opts_chunk$set(eval = T, echo = TRUE)
```

## Preparing documents 
Please read [Preparation](Preparation.html) for the three data types that **keyATM** can read. **keyATM** package includes a tidy dataset for illustration purpose. In this example, we use ***. You can load this data by `data(keyATM_data_bills)`.

```{r, warning=FALSE, message=FALSE, fig.align='center'}
library(keyATM)
data(keyATM_data_bills)

library(quanteda)
bills_dfm <- keyATM_data_bills$doc_dfm  # quanteda object
keyATM_docs <- keyATM_read(bills_dfm)
```

## Preparing time index
HMM model needs a vector of time indexes. This is an "index" and not the actual time stamps (year and date). For example, `bills` data contain session information, which ranges from `101` to `114`. 

```{r, warning=FALSE, message=FALSE, fig.align='center'}
bills_time_index <- keyATM_data_bills$time_index
table(bills_time_index)
```

Time index should start from `1`, increment by $1$, and have the same value if they are in the same time (for example the session of congress).
```{r, warning=FALSE, message=FALSE, fig.align='center'}
bills_time_index <- as.integer(bills_time_index - 100)
table(bills_time_index)
```

## Keywords

We set four keyword-topics. Keywrods should be stored in a list. Each element in the list is a character vector, which corresponds to a single keyword-topic.
```{r, eval=T, warning=FALSE, message=FALSE, fig.align='center'}
bills_keywords <- list(
                       Education = c("education", "child", "student"),
                       Law       = c("court", "law", "attorney"),
                       Health    = c("public", "health", "program"),
                       Drug      = c("drug", "treatment")
                      )
```

## Checking keywords
Before you fit the model, please make sure your keywords appear enough in your corpus. [FAQ](FAQ.html#how-to-select-keywords) explains what could be good keywords. This step is the same as the [Base model](keyATM_basic.html#checking-keywords).


## Fitting the model
```{r, warning=FALSE, message=FALSE, fig.align='center'}
out <- keyATM(    
              docs              = keyATM_docs,    # text input
              no_keyword_topics = 3,              # number of topics without keywords
              keywords          = bills_keywords, # keywords
              model             = "dynamic",          # select the model
              model_settings    = list(time_index = bills_time_index,
                                       num_states = 5),
              options           = list(seed = 100)
             )
```

## Saving the model

Once you fit the model, you can save the model with `save()` for replication. This is the same as the [Base model](keyATM_basic.html#saving-the-model).

## Checking top words
```{r, warning=FALSE, message=FALSE, fig.align='center'}
top_words(out)
```


