---
title: "keyATM Label"
output: 
  html_document:
    toc: true
---

```{r setup II, include=FALSE, eval=TRUE}
knitr::opts_chunk$set(eval = T, echo = TRUE)
```

## Preparing documents and time index
Please read [Preparation](Preparation.html) for the reading of documents and creating a list of keywords. We use bills data we prapared ([documents](Preparation.html#reading-documents-into-keyatm) and [keywords](Preparation.html#preparing-keywords)).


```{r, include = T, warning=FALSE, message=FALSE, fig.align='center'}
library(keyATM)
library(quanteda)

data(keyATM_data_bills)
bills_keywords <- keyATM_data_bills$keywords
bills_dfm <- keyATM_data_bills$doc_dfm  # quanteda dfm object
keyATM_docs <- keyATM_read(bills_dfm)
```

Label model needs a vector of labels. Values of the vector represent topics. If a document is missing a label, the label vector should have `NA`. 

```{r, warning=FALSE, message=FALSE, fig.align='center'}
labels_use <- keyATM_data_bills$labels
labels_use
length(labels_use)  # should be the same as the number of documents
```

Please make sure that **the order of label index is the same as the order of documents**.

## Fitting the model
```{r, warning=FALSE, message=FALSE, fig.align='center'}
out <- keyATM(
              docs              = keyATM_docs,                # text input
              no_keyword_topics = 3,                          # number of topics without keywords
              keywords          = bills_keywords,             # keywords
              model             = "label",                    # select the model
              model_settings    = list(labels = labels_use),  # set labels
              options           = list(seed = 250)
             )
```

## Saving the model

Once you fit the model, you can save the model with `save()` for replication. This is the same as the [Base model](keyATM_base.html#saving-the-model).

## Checking top words
```{r, warning=FALSE, message=FALSE, fig.align='center'}
top_words(out)
```


