---
title: "keyATM Dynamic"
output: 
  html_document:
    toc: true
---

```{r setup II, include=FALSE, eval=TRUE}
knitr::opts_chunk$set(eval = T, echo = TRUE)
```

\newcommand{\btheta}{\boldsymbol{\theta}}
\newcommand{\bbeta}{\boldsymbol{\beta}}
\newcommand{\balpha}{\boldsymbol{\alpha}}
\newcommand{\bsigma}{\boldsymbol{\sigma}}
\newcommand{\bgamma}{\boldsymbol{\gamma}}
\newcommand{\blambda}{\boldsymbol{\lambda}}
\newcommand{\bphi}{\boldsymbol{\phi}}
\newcommand{\bpsi}{\boldsymbol{\psi}}
\newcommand{\bpi}{\boldsymbol{\pi}}


```{r, include=FALSE, warning=FALSE, message=FALSE, fig.align='center'}
library(keyATM)
library(quanteda)
library(magrittr)
library(dplyr)
library(tibble)
data(data_corpus_inaugural, package = "quanteda")

data_tokens <- tokens(data_corpus_inaugural,
                      remove_numbers = TRUE, 
                      remove_punct = TRUE, 
                      remove_symbols = TRUE,
                      remove_separators = TRUE,
                      remove_url = TRUE) %>%
                 tokens_tolower() %>%
                 tokens_remove(c(stopwords("english"), 
                               "may", "shall", "can",
                               "must", "upon", "with", "without")) %>%
                 tokens_select(min_nchar = 3)
                
data_dfm <- dfm(data_tokens) %>%
               dfm_trim(min_termfreq = 5, min_docfreq = 2)

keywords <- list(Government     = c("laws", "law", "executive"),
                 Congress       = c("congress", "party"),
                 Peace          = c("peace", "world", "freedom"),
                 Constitution   = c("constitution", "rights"),
                 ForeignAffairs  = c("foreign", "war"))

keyATM_docs <- keyATM_read(data_dfm)
```


Researchers are often interested in investigating how the prevalence of topics change
over time. The **keyATM** can use time stamps for the prior for
document-topic distribution through Hidden Markov Model ([Chib 1998](https://doi.org/10.1016/S0304-4076(97)00115-2)).

Section 4 of [Eshima et al. (2020)](https://arxiv.org/abs/2004.05964) explains the dynamic keyATM in details.
As explained in [keyATM Covariates](keyATM_cov.html), we recommend researchers to
construct a numeric or an integer vector of time stamps after preprocessing texts. 

## Preparing time index
Please read [Preparation](Preparation.html) for the reading of documents and creating a list of keywords. 

We use the US Presidential inaugural address data we prapared ([documents](Preparation.html#preparing-texts) and [keywords](Preparation.html#preparing-keywords)).


```{r, include = T, warning=FALSE, message=FALSE, fig.align='center'}
# Get meta information (time stamp)
vars <- docvars(data_corpus_inaugural)
head(vars)

# Divide by a decade
# Timestamp should start with 1 (the variable "Period")
vars %>%
  as_tibble() %>%
  mutate(Period = (vars$Year - 1780) %/% 10 + 1) -> vars_period
vars_period %>% select(Year, Period)
```
The time index (`Period`) should start from `1` and increment by 1 (ascending order).
To properly process date, please consider using the [lubridate](https://lubridate.tidyverse.org/) package.

We pass the time index to the `keyATM()` function, specifying
the number of hidden states with the `num_states` in the
`model_settings` argument.


```{r, warning=FALSE, message=FALSE, fig.align='center'}
out <- keyATM(docs              = keyATM_docs,                         
              no_keyword_topics = 3,                                   
              keywords          = keywords,                      
              model             = "dynamic",                           
              model_settings    = list(time_index = vars_period$Period,
                                       num_states = 5),                
              options           = list(seed = 250))
```


## Interpreting results
We can use the `top_words()`, `top_docs()`, `plot_modelfit()`, `plot_alpha()`,
and `plot_pi()` functions
as in [the base keyATM](keyATM_base.html). 

```{r, warning=FALSE, message=FALSE, fig.align='center'}
top_words(out)
```

Since each state has a unique prior for the document-topic distributions, the `plot_alpha()`
function produces a different figure from [the base keyATM](keyATM_base.html).

```{r, warning=FALSE, message=FALSE, fig.align='center'}
fig_alpha <- plot_alpha(out)
fig_alpha
```

Finally, we can plot the time trend of topics with the `plot_timetrend()` function.
With the `time_index_label` argument, you can label each time index. Note that `store_theta` option
in the `keyATM()` function should be `TRUE` to show 90% credible intervals.

```{r, warning=FALSE, message=FALSE, fig.align='center'}
out <- keyATM(docs              = keyATM_docs,                         
              no_keyword_topics = 3,                                   
              keywords          = keywords,                      
              model             = "dynamic",                           
              model_settings    = list(time_index = vars_period$Period,
                                       num_states = 5),                
              options           = list(seed = 250, store_theta = TRUE, thinning = 5))
fig_timetrend <- plot_timetrend(out, time_index_label = vars$Year, xlab = "Year", width = 5)
fig_timetrend
```


## Reference
* Chib, S. (1998). "Estimation and comparison of multiple change-point models." *Journal of econometrics*, 86(2), 221-241.
* Eshima, S., Imai, K., & Sasaki, T. (2020). Keyword Assisted Topic Models. arXiv preprint arXiv:2004.05964.
