---
title: "keyATM Dynamic"
output: 
  html_document:
    toc: true
---

```{r setup II, include=FALSE, eval=TRUE}
knitr::opts_chunk$set(eval = T, echo = TRUE)
```

## Preparing documents and time index
Please read [Preparation](Preparation.html) for the reading of documents and creating a list of keywords. We use bills data we prapared ([documents](Preparation.html#reading-documents-into-keyatm) and [keywords](Preparation.html#preparing-keywords)).


```{r, include = T, warning=FALSE, message=FALSE, fig.align='center'}
library(keyATM)
library(quanteda)

data(keyATM_data_bills)
bills_keywords <- keyATM_data_bills$keywords
bills_dfm <- keyATM_data_bills$doc_dfm  # quanteda dfm object
keyATM_docs <- keyATM_read(bills_dfm)
```

HMM model needs a vector of time indexes. This is an "index" and not the actual time stamps (year and date). For example, `bills` data contain session information, which ranges from `101` to `114`. 

```{r, warning=FALSE, message=FALSE, fig.align='center'}
bills_time_index <- keyATM_data_bills$time_index
table(bills_time_index)
```

Time index should start from `1`, increment by $1$, and have the same value if they are in the same time (for example the session of congress).
```{r, warning=FALSE, message=FALSE, fig.align='center'}
bills_time_index <- as.integer(bills_time_index - 100)
table(bills_time_index)
```

Please make sure that **the order of time index is the same as the order of documents**.

## Fitting the model
Researchers need to specify the number of states in addition to keywords.

```{r, warning=FALSE, message=FALSE, fig.align='center'}
out <- keyATM(    
              docs              = keyATM_docs,                         # text input
              no_keyword_topics = 3,                                   # number of topics without keywords
              keywords          = bills_keywords,                      # keywords
              model             = "dynamic",                           # select the model
              model_settings    = list(time_index = bills_time_index,  # time index
                                       num_states = 5),                # number of (latent) states in the model 
              options           = list(seed = 250)
             )
```

## Saving the model

Once you fit the model, you can save the model with `save()` for replication. This is the same as the [Base model](keyATM_base.html#saving-the-model).

## Checking top words
```{r, warning=FALSE, message=FALSE, fig.align='center'}
top_words(out)
```


