---
title: "keyATM Base"
output: 
  html_document:
    toc: true
---

```{r setup II, include=FALSE, eval=TRUE}
knitr::opts_chunk$set(eval = T, echo = TRUE)
```

## Preparing documents and keywords
Please read [Preparation](Preparation.html) for the reading of documents and creating a list of keywords. We use bills data we prapared ([documents](Preparation.html#reading-documents-into-keyatm) and [keywords](Preparation.html#preparing-keywords)).

```{r, include = T, warning=FALSE, message=FALSE, fig.align='center'}
library(keyATM)
library(quanteda)

data(keyATM_data_bills)
bills_keywords <- keyATM_data_bills$keywords
bills_dfm <- keyATM_data_bills$doc_dfm  # quanteda dfm object
keyATM_docs <- keyATM_read(bills_dfm)
```


## Fitting the model
```{r, warning=FALSE, message=FALSE, fig.align='center', results="hide"}
out <- keyATM(docs              = keyATM_docs,    # text input
              no_keyword_topics = 3,              # number of topics without keywords
              keywords          = bills_keywords, # keywords
              model             = "base",         # select the model
              options           = list(seed = 50)
             )
```
The default number of iterations is `1500`. Please check [this page](Options.html) for available options.


## Saving the model

Once you fit the model, you can save the model with `save()` for replication.
```{r, eval=F, warning=FALSE, message=FALSE, fig.align='center'}
save(out, file="SAVENAME.rds")
```

To load the model, you can use `readRDS()` function.
```{r, eval=F, warning=FALSE, message=FALSE, fig.align='center'}
out <- readRDS(file="SAVENAME.rds")
```

## Checking top words
```{r, warning=FALSE, message=FALSE, fig.align='center'}
top_words(out)
```


