---
title: "keyATM Covariates"
output:
  html_document:
    toc: true
---

```{r setup II, include=FALSE, eval=TRUE}
knitr::opts_chunk$set(eval = TRUE, echo = TRUE)
```

```{r, include=FALSE, warning=FALSE, message=FALSE}
library(keyATM)
library(quanteda)
library(magrittr)
data(data_corpus_inaugural, package = "quanteda")
data_corpus_inaugural <- head(data_corpus_inaugural, n = 58)

data_tokens <- tokens(data_corpus_inaugural,
                      remove_numbers = TRUE,
                      remove_punct = TRUE,
                      remove_symbols = TRUE,
                      remove_separators = TRUE,
                      remove_url = TRUE) %>%
                 tokens_tolower() %>%
                 tokens_remove(c(stopwords("english"),
                               "may", "shall", "can",
                               "must", "upon", "with", "without")) %>%
                 tokens_select(min_nchar = 3)

data_dfm <- dfm(data_tokens) %>%
               dfm_trim(min_termfreq = 5, min_docfreq = 2)

keywords <- list(Government     = c("laws", "law", "executive"),
                 Congress       = c("congress", "party"),
                 Peace          = c("peace", "world", "freedom"),
                 Constitution   = c("constitution", "rights"),
                 ForeignAffairs  = c("foreign", "war"))

keyATM_docs <- keyATM_read(data_dfm)
```

Scholars often have meta information about documents (e.g., authorship).
The **keyATM** provides a way to incorporate covariate for document-topic distribution, using a
Dirichlet-Multinomial regression ([Mimno and McCallum 2008](https://dl.acm.org/doi/abs/10.5555/3023476.3023525)).
Section 3 of <a href="https://doi.org/10.1111/ajps.12779" target="_blank">Eshima et al. (2024)</a> explains the covariate keyATM in details.


## Preparing covariates
We follow the same procedure for the text preparation
explained in [Preparation](Preparation.html) and explain
how to prepare covariates in this section.

The `docvars()` function in the **quanteda** package is especially useful
to construct a `vector` or a `dataframe` of covariates because it ensures that
documents and covariates are corresponding to each other.
Since the **keyATM** does not take missing values,
we recommend researchers to remove any missing values from
covariates before extracting them using the `docvars()`.

Moreover, we strongly recommend researchers to
extract covariates *after* preprocessing texts
because preprocessing steps will remove documents without any terms,
which may result in any discrepancies between documents and covariates.

Therefore, the recommended procedure is
(1) removing missing values from covariates, (2) preprocessing texts
(including the process to discard documents that do not contain any words),
and (3) extracting covariates using `docvars()` function.

In this example, we create a period dummy and a party dummy from the corpus
and use them as covariates for the covariate keyATM.
First, we extract covariates attached to each document in the corpus
with the `docvars()` function.

```{r, warning=FALSE, message=FALSE}
vars <- docvars(data_corpus_inaugural)
head(vars)
```

There are six unique parties and 58 unique years. We categorize them
and create a new set of covariates. First, we divide years into two
period, before and after 1900. Then, we categorize parties into Democratic,
Republican, and Others.
```{r, warning=FALSE, message=FALSE}
library(dplyr)
vars %>%
  as_tibble() %>%
  mutate(Period = case_when(Year <= 1899 ~ "18_19c",
                            TRUE ~ "20_21c")) %>%
  mutate(Party = case_when(Party == "Democratic" ~ "Democratic",
                           Party == "Republican" ~ "Republican",
                           TRUE ~ "Other")) %>%
  select(Party, Period) -> vars_selected
table(vars_selected)
```

Since we have categorical variables, we set baselines with the `factor()` function.
```{r, warning=FALSE, message=FALSE}
vars_selected %>%
  mutate(Party  = factor(Party,
                         levels = c("Other", "Republican", "Democratic")),
         Period = factor(Period,
                         levels = c("18_19c", "20_21c"))) -> vars_selected
```

The **keyATM** internally uses the `model.matrix()` function so that researchers can pass
a formula to model covariates
(for more detailed information, refer to [formula](https://rdrr.io/r/stats/formula.html)).
For example, in this example, we have a following matrix.
```{r, warning=FALSE, message=FALSE}
head(model.matrix(~ Party + Period, data = vars_selected))
```

## Fitting the model
We fit the model with the `keyATM()` function, passing covariates data
and the formula with the `model_settings` argument.
The text data is the same as what we use in the [base model](keyATM_base.html).
Please check [this page](Options.html) for available options.
```{r, warning=FALSE, message=FALSE, results="hide"}
out <- keyATM(
  docs              = keyATM_docs,
  no_keyword_topics = 5,
  keywords          = keywords,
  model             = "covariates",
  model_settings    = list(covariates_data    = vars_selected,
                           covariates_formula = ~ Party + Period),
  options           = list(seed = 250)
)
```

Once you fit the model, you can save the model with `saveRDS()` for replication. This is the same as the [base model](keyATM_base.html#saving-the-model).

You can [resume](Resume.html) the iteration by specifying the `resume` argument.

**keyATM** automatically standardizes non-factor covariates. The `standardize` option in `model_settings` argument of the `keyATM()` function now takes one of `"all"`, `"none"`, or `"non-factor"` (default). `"all"` standardizes all covariates (except the intercept), `"none"` does not standardize any covariates, and `"non-factor"` standardizes non-factor covariates.


## Interpreting results
We can use the `top_words()`, `top_docs()`,  `plot_modelfit()`, and `plot_pi()` functions
as in the base keyATM. The `plot_alpha()` is not defined for the covariate keyATM because
we use covariates to model the prior for the document-topic distribution
and $\alpha$ does not explicitly appear in the model.

### Getting covariates from the output object
First, we use the output from the [previous section](keyATM_cov.html#fitting-the-model) and check the
covariates used in the model. Note that covariates are standardized by default
(i.e., each covariates to have zero mean and a standard deviation one).

This transformation does not change the substantive results as it is a
linear transformation.
Researchers can use raw values with `standardize = FALSE` in the `model_settings`
argument.

Researchers can glance covariate information with the
`covariates_info()` and the `covariates_get()` function
will return covariates used in the fitted output.

```{r, warning=FALSE, message=FALSE}
covariates_info(out)
```

```{r, warning=FALSE, message=FALSE}
used_covariates <- covariates_get(out)
head(used_covariates)
```

### Covariates and document-topic distributions
The covariate keyATM can characterize the relations between covariates
and document-topic distributions. We can obtain the marginal posterior mean of
document-topic distribution conditioned on the covariates.

Suppose that we want to know document-topic distributions for each period.
We use a binary variable `Period20_21c`, which indicates the period
for this purpose.

The `by_strata_DocTopic()` function can display the marginal posterior means of
document-topic distributions for each value of (discrete) covariates.

In the `by_strata_DocTopic()` function, we specify the variable we focus on
in `by_var` argument and label each value in the variable (ascending order).

In this case, the `Period20_21c` equals zero indicates speeches in the 18th
and 19th century and equals one for the speeches in the 20th and 21st century.
```{r, warning=FALSE, message=FALSE}
strata_topic <- by_strata_DocTopic(
  out, by_var = "Period20_21c",
  labels = c("18_19c", "20_21c")
)
```

We can visualize results with the `plot()` function.
The figure shows the marginal posterior means of document-topic distributions and
the 90% credible intervals of them for each value of covariates.

The figure indicates that both topics are more likely to
appear in the 18th and 19th century.
```{r, warning=FALSE, message=FALSE, fig.align='center'}
fig_doctopic <- plot(strata_topic, var_name = "Period", show_topic = c(4, 5))
fig_doctopic
```

The figure can be saved with the `save_fig()` function.
```{r, eval=FALSE, warning=FALSE, message=FALSE}
save_fig(fig_doctopic, "figures/doctopic.pdf", width = 7, height = 3.5)
```

We can visualize results by covariate with `by = "covariate"` argument.
The plot below combines two panels in the previous plot and
display in the same panel.
```{r, message=FALSE, warning=FALSE, fig.align='center'}
fig_doctopic <- plot(
  strata_topic, var_name = "Period",
  show_topic = c(4, 5), by = "covariate"
)
```

Using the output of the `keyATM`, we can calculate 90% credible intervals
of the differences in the
mean of document-topic distribution.

Since we set the 18th and 19th century dummy as the
baseline when constructing `factor` for this variable,
the comparison is the relative increase or decrease
from the 18th and 19th century to the 20th and 21st century.
```{r, warning=FALSE, message=FALSE}
theta1 <- strata_topic$theta[[1]]  # 18_19c
theta2 <- strata_topic$theta[[2]]  # 20_21c
theta_diff <- theta1[, c(4, 5)] - theta2[, c(4, 5)]  # focus on two topics
theta_diff_quantile <- apply(theta_diff, 2, quantile, c(0.05, 0.5, 0.95))
theta_diff_quantile
```


Furthermore, we can use the `predict()` function to get the predicted mean of
the document-topic distribution for three party categories.
```{r, warning=FALSE, message=FALSE, fig.align='center'}
strata_rep <- by_strata_DocTopic(
  out, by_var = "PartyRepublican",
  labels = c("Non-Republican", "Republican")
)
strata_dem <- by_strata_DocTopic(
  out, by_var = "PartyDemocratic",
  labels = c("Non-Democratic", "Democratic")
)

est_rep <- summary(strata_rep)[["Republican"]]  # Republican data
est_dem <- summary(strata_dem)[["Democratic"]]  # Democratic data
```

Now we are missing the baseline (Others).
```{r, warning=FALSE, message=FALSE, fig.align='center'}
new_data <- covariates_get(out)

# Setting both Republican and Democratic dummy to 0 means `Others`
new_data[, "PartyRepublican"] <- 0
new_data[, "PartyDemocratic"] <- 0
pred <- predict(out, new_data, label = "Others")
```

Now, we combine three objects and make a plot.
```{r, warning=FALSE, message=FALSE, fig.align='center'}
res <- bind_rows(est_rep, est_dem, pred) %>%
          filter(TopicID %in% c(4, 5))  # Select two topics
labels <- unique(res$label)

library(ggplot2)
ggplot(res, aes(x = label, ymin = Lower, ymax = Upper, group = Topic)) +
  geom_errorbar(width = 0.1) +
  coord_flip() +
  facet_wrap(~Topic) +
  geom_point(aes(x = label, y = Point)) +
  scale_x_discrete(limits = rev(labels)) +
  xlab("Party") +
  ylab(expression(paste("Mean of ", theta))) +
  theme_bw()
```


### Covariates and topic-word distribution
Although the covariate keyATM does not directly model topic-word distributions,
the model can examine how topic-word distributions change across different values
of document-level covariates. For this analysis, we need to use the `keep` argument in
the `keyATM()` function to store `Z` and `S`.
Then we pass the output with these stored values to the `by_strata_TopicWord()` function.
The example below demonstrates top words associated to each topic for speeches from
different parties using the `Party` covariate.

```{r, warning=FALSE, message=FALSE, results='hide'}
out <- keyATM(
  docs              = keyATM_docs,
  no_keyword_topics = 5,
  keywords          = keywords,
  model             = "covariates",
  model_settings    = list(covariates_data    = vars_selected,
                           covariates_formula = ~ Party + Period),
  options           = list(seed = 250),
  keep              = c("Z", "S")
)
strata_tw <- by_strata_TopicWord(
  out, keyATM_docs,
  by = as.vector(vars_selected$Party)
)
```

We check the result.
```{r, warning=FALSE, message=FALSE}
top_words(strata_tw, n = 3)
```

## keyATM Covariate with Pólya-Gamma Augmentation
An alternative modeling approach is to use the Pólya-Gamma augmentation for topic
assignments. This approach has a speed advantage (computational time does not significantly
change by the number of covariates), but estimated topics can be
sensitive to the order.
Please read [technical details](keyATMPG.html) before use this option.

To estimate keyATM Covariate with the Pólya-Gamma augmentation, set `covariates_model = "PG"`.
```{r, warning=FALSE, message=FALSE, fig.align='center'}
out <- keyATM(
  docs              = keyATM_docs,
  no_keyword_topics = 5,
  keywords          = keywords,
  model             = "covariates",
  model_settings    = list(covariates_data    = vars_selected,
                           covariates_formula = ~ Party + Period,
                           covariates_model = "PG"),
  options           = list(seed = 250)
)
top_words(out)
```

## Reference
* Eshima, S., Imai, K., & Sasaki, T. (2024). "Keyword Assisted Topic Models." *American Journal of Political Science* 68(2): 730-750.
* Mimno D. McCallum A. (2008). “Topic models conditioned on arbitrary features with Dirichlet-Multinomial regression.” In *Proceedings of the 24th Conference on Uncertainty in Artificial Intelligence*, pp. 411-418.
