---
title: "keyATM Covariate"
output: 
  html_document:
    toc: true
---

```{r setup II, include=FALSE, eval=TRUE}
knitr::opts_chunk$set(eval = F, echo = TRUE)
```

## Preparing documents and covariates
Please read [Preparation](Preparation.html) for the three data types that **keyATM** can read. **keyATM** package includes a tidy dataset for illustration purpose. In this example, we use ***. You can load this data by `data(keyATM_data_bills)`.

```{r, warning=FALSE, message=FALSE, fig.align='center'}
library(keyATM)
data(keyATM_data_bills)

library(quanteda)
bills_dfm <- keyATM_data_bills$doc_dfm  # quanteda object
keyATM_docs <- keyATM_read(bills_dfm)
```

**keyATM** takes `matrix` type data. If you have $D$ documents and $C$ covariates, the matrix should be $D \times C$. In this example, we have a dummy variable that indicates ...

```{r, warning=FALSE, message=FALSE, fig.align='center'}
bills_cov <- keyATM_data_bills$cov
dim(bills_cov)  # We have 140 documents and a single covariate
```


## Keywords

We set four keyword-topics. Keywrods should be stored in a list. Each element in the list is a character vector, which corresponds to a single keyword-topic.
```{r, eval=T, warning=FALSE, message=FALSE, fig.align='center'}
bills_keywords <- list(
                       Education = c("education", "child", "student"),
                             Law = c("court", "law", "attorney"),
                          Health = c("public", "health", "program"),
                            Drug = c("drug", "treatment")
                      )
```


## Checking keywords
Before you fit the model, please make sure your keywords appear enough in your corpus. [FAQ](FAQ.html#how-to-select-keywords) explains what could be good keywords. This step is the same as [basic model](keyATM_basic.html#checking-keywords).


## Fitting the model
```{r, warning=FALSE, message=FALSE, fig.align='center', results="hide"}
out <- keyATM(    
                  keyATM_docs = keyATM_docs,    # text input
                    regular_k = 3,              # number of regular topics
                     keywords = bills_keywords, # keywords
                        model = "cov",        # select the model
               model_settings = list(covariates_data = bills_cov),
                      options = list(seed = 100)
              )
```
The default number of iterations is `1500`. Please check [this page](Options.html) for available options.


## Saving the model

Once you fit the model, you can save the model with `save()` for replication. This is the same as [basic model](keyATM_basic.html#saving-the-model).

## Checking top words
```{r, warning=FALSE, message=FALSE, fig.align='center'}
top_words(out)
```



