---
title: "keyATM Covariates"
output: 
  html_document:
    toc: true
---

```{r setup II, include=FALSE, eval=TRUE}
knitr::opts_chunk$set(eval = T, echo = TRUE)
```

## Preparing documents and covariates
Please read [Preparation](Preparation.html) for the reading of documents and creating a list of keywords. We use bills data we prapared ([documents](Preparation.html#reading-documents-into-keyatm) and [keywords](Preparation.html#preparing-keywords)).

```{r, include = T, warning=FALSE, message=FALSE, fig.align='center'}
library(keyATM)
library(quanteda)

data(keyATM_data_bills)
bills_keywords <- keyATM_data_bills$keywords
bills_dfm <- keyATM_data_bills$doc_dfm  # quanteda dfm object
keyATM_docs <- keyATM_read(bills_dfm)
```

For the covariate data, we use the dummy variable which takes one if the bill is proposesd by the Republican party and zero otherwise (Adler and Wilkerson 2018). **keyATM** takes `matrix` or `data.frame` (`tibble`) type covariates data. If you have $D$ documents and $M$ covariates, the matrix should be $D \times M$. In this example, we have a dummy variable that indicates party identification.

```{r, warning=FALSE, message=FALSE, fig.align='center'}
bills_cov <- keyATM_data_bills$cov # dummy variable indicating the party proposed the bill
dim(bills_cov)  # We have 140 documents and a single covariate for each document
```

Please make sure that **the order of covariates is the same as the order of documents**.




## Fitting the model
```{r, warning=FALSE, message=FALSE, fig.align='center', results="hide"}
out <- keyATM(
              docs              = keyATM_docs,                            # text input
              no_keyword_topics = 3,                                      # number of topics without keywords
              keywords          = bills_keywords,                         # keywords (a list)
              model             = "covariates",                           # select the model
              model_settings    = list(covariates_data    = bills_cov,    # covariate data
                                       covariates_formula = ~ RepParty,   # formula to fit covarite
                                       mh_use             = FALSE),       # use Metloporis Hastings
              options           = list(seed = 250)
             )
```
The `covariates_formula` takes the same form of a [`formula`](https://rdrr.io/r/stats/formula.html) for `model.matrix()` function. You do not need to specify the left hand side of the formula. The default number of iterations is `1500`. Please check [this page](Options.html) for available options.

If you set `mh_use = TRUE`, the estimation process will speed up.


## Saving the model

Once you fit the model, you can save the model with `save()` for replication. This is the same as the [Base model](keyATM_base.html#saving-the-model).

## Checking top words
```{r, warning=FALSE, message=FALSE, fig.align='center'}
top_words(out)
```

## Reference
```
Adler, E Scott and John Wilkerson. 2018. ``Congressional bills project.'' NSF 880066 and 0080061:213–227.
```


