---
title: "keyATM Basic"
output: 
  html_document:
    toc: true
---

```{r setup II, include=FALSE, eval=TRUE}
knitr::opts_chunk$set(eval = T, echo = TRUE)
```

## Preparing documents
Please read [Preparation](Preparation.html) for the three data types that **keyATM** can read. **keyATM** package includes a tidy dataset for illustration purpose. In this example, we use ***. You can load this data by `data(keyATM_data_bills)`.

```{r, warning=FALSE, message=FALSE, fig.align='center'}
library(keyATM)
data(keyATM_data_bills)
```


## Keywords

We set four keyword-topics. Keywrods should be stored in a list. Each element in the list is a character vector, which corresponds to a single keyword-topic.
```{r, eval=T, warning=FALSE, message=FALSE, fig.align='center'}
bills_keywords <- list(
                       Education = c("education", "child", "student"),
                       Law       = c("court", "law", "attorney"),
                       Health    = c("public", "health", "program"),
                       Drug      = c("drug", "treatment")
                      )
```


## Reading documents
Before fitting the model, we need to read texts and keywords into **keyATM**. Here we use **quanteda**'s `dfm`.


```{r, warning=FALSE, message=FALSE, fig.align='center'}
library(quanteda)
bills_dfm <- keyATM_data_bills$doc_dfm  # quanteda object
keyATM_docs <- keyATM_read(bills_dfm)
```


## Checking keywords
Before you fit the model, please make sure your keywords appear enough in your corpus. [FAQ](FAQ.html#how-to-select-keywords) explains what could be good keywords.
```{r, warning=FALSE, message=FALSE, fig.align='center', height=3, width=3}
visualize_keywords(keyATM_docs, bills_keywords)
```



## Fitting the model
```{r, warning=FALSE, message=FALSE, fig.align='center', results="hide"}
out <- keyATM(keyATM_docs       = keyATM_docs,    # text input
              no_keyword_topics = 3,              # number of regular topics
              keywords          = bills_keywords, # keywords
              model             = "basic",        # select the model
              options           = list(seed = 100)
             )
```
The default number of iterations is `1500`. Please check [this page](Options.html) for available options.


## Saving the model

Once you fit the model, you can save the model with `save()` for replication.
```{r, eval=F, warning=FALSE, message=FALSE, fig.align='center'}
save(out, file="SAVENAME.rds")
```

To load the model, you can use `load()` function.
```{r, eval=F, warning=FALSE, message=FALSE, fig.align='center'}
out <- load(file="SAVENAME.rds")
```

## Checking top words
```{r, warning=FALSE, message=FALSE, fig.align='center'}
top_words(out)
```


