---
title: "keyATM Covariates"
output: 
  html_document:
    toc: true
---

```{r setup II, include=FALSE, eval=TRUE}
knitr::opts_chunk$set(eval = T, echo = TRUE)
```

## Preparing documents and covariates
Please read [Preparation](Preparation.html) for the reading of documents and creating a list of keywords. We use bills data we prapared ([documents](Preparation.html#reading-documents-into-keyatm) and [keywords](Preparation.html#preparing-keywords)).

**keyATM** takes `matrix` type covariates data. If you have $D$ documents and $C$ covariates, the matrix should be $D \times C$. In this example, we have a dummy variable that indicates ...

```{r, warning=FALSE, message=FALSE, fig.align='center'}
library(keyATM)
data(keyATM_data_bills)
bills_cov <- keyATM_data_bills$cov
dim(bills_cov)  # We have 140 documents and a single covariate
```


```{r, include = F, warning=FALSE, message=FALSE, fig.align='center'}
library(quanteda)
bills_dfm <- keyATM_data_bills$doc_dfm  # quanteda object
keyATM_docs <- keyATM_read(bills_dfm)

bills_keywords <- list(
                       Education = c("education", "child", "student"),
                       Law       = c("court", "law", "attorney"),
                       Health    = c("public", "health", "program"),
                       Drug      = c("drug", "treatment")
                      )
```


## Fitting the model
```{r, warning=FALSE, message=FALSE, fig.align='center', results="hide"}
out <- keyATM(    
              docs              = keyATM_docs,    # text input
              no_keyword_topics = 3,              # number of topics without keywords
              keywords          = bills_keywords, # keywords
              model             = "covariates",   # select the model
              model_settings    = list(covariates_data = bills_cov),
              options           = list(seed = 100, store_theta = TRUE)
             )
```
The default number of iterations is `1500`. Please check [this page](Options.html) for available options. If you want to regress covariates on the document topic proportion, please use `store_theta` option.


## Saving the model

Once you fit the model, you can save the model with `save()` for replication. This is the same as the [Base model](keyATM_basic.html#saving-the-model).

## Checking top words
```{r, warning=FALSE, message=FALSE, fig.align='center'}
top_words(out)
```

## Regressing covariates on document topic proportion

```{r, warning=FALSE, message=FALSE, fig.align='center'}
coef <- get_coefficients(out, covariates_data = bills_cov)
plot(coef, topics = 1:3, variables = c("RepParty"))
```

