---
title: "Preparation"
output: 
  html_document:
    toc: false
---

## Preparing Texts
To fit topic models with **keyATM**, users need to transform their text data using `keyATM_read()`. 
This page explains three ways to input text data into `keyATM_read()`. 

### Using quanteda dfm (**recommended**)
**keyATM** can read a document-feature matrix (`dfm` object) created by **quanteda** package (**this method is strongly recommended**). Since **keyATM** does not provide preprocessing functions, we recommend users to preprocess texts with **quanteda**. 
By making a `token` object from a `corpus` object, **quanteda** can perform various preprocessing methods ([quanteda Quick Start: Tokenizing texts](https://quanteda.io/articles/quickstart.html#tokenizing-texts)). 
Users can create a `dfm` object from a `token` object.

#### Loading data for **quanteda**
Here is an example of loading text data and transform it into the **quanteda** `corpus` format.
We use the **readtext** package in this example.
```{r, eval=FALSE, warning=FALSE, message=FALSE, fig.align='center'}
library(quanteda)
library(readtext)

# Read text files
raw_docs <- readtext("PATH_TO_THE_FOLDER/*.txt",
                     encoding = "UTF-8")

# Preprocessing with quanteda and create a dfm object
key_corpus <- corpus(raw_docs, text_field = "text")

# If you use the covariate model, please consider using `docvars` argument
key_corpus <- corpus(raw_docs, text_field = "text", docvars = COVARIATES)

# You can conduct a variety of preprocessing in this step as shown in the next section
key_token <- tokens(key_corpus)

# Create a document-feature matrix (a dfm object) from a token object
key_dfm <- dfm(key_token)
```

#### Preprocessing data
We show a concrete example of preprocessing data and loading it into the **keyATM**. 
We use the US presidential inaugural address data that is one of the built-in datasets of the **quanteda**.
```{r, warning=FALSE, message=FALSE, fig.align='center'}
library(keyATM)
library(quanteda)
library(magrittr)
data(data_corpus_inaugural, package = "quanteda")
data_corpus_inaugural <- head(data_corpus_inaugural, n = 58)
```

Since the US presidential speech dataset is a `corpus` object, we use the `tokens()` function to convert this data
into a `token` object and to preprocess texts before creating a `dfm` object.
The `tokens()` and related functions in the **quanteda** provide various preprocessing functions. Preprocessing can reduce the number of unique features (words) in the corpus, which is critical for increasing the interpretability. In the example below, we adopt some of the most common preprocessing steps.
```{r, warning=FALSE, message=FALSE, fig.align='center'}
data_tokens <- tokens(data_corpus_inaugural,
                      remove_numbers = TRUE, 
                      remove_punct = TRUE, 
                      remove_symbols = TRUE,
                      remove_separators = TRUE,
                      remove_url = TRUE) %>%
                 tokens_tolower() %>%
                 tokens_remove(c(stopwords("english"), 
                               "may", "shall", "can",
                               "must", "upon", "with", "without")) %>%
                 tokens_select(min_nchar = 3)
```
The `tokens()` function removes punctuations and unnecessary characters, 

The `tokens_tolower()` function converts all characters into lower cases,
The `tokens_remove()` function removes general stop words (e.g, the, is, at, with `stopwords("english")`)
and corpus specific high frequent words ("may", "shall", ..., "without" in this example), 
and `tokens_select` drops
short words that do not usually contribute to interpreting topics.

Before loading data into the **keyATM**, we construct a document-feature matrix (`dfm` object) 
with the `dfm()` function in the **quanteda**. We trim infrequent terms with the `dfm_trim()` function.

```{r, warning=FALSE, message=FALSE}
data_dfm <- dfm(data_tokens) %>%
              dfm_trim(min_termfreq = 5, min_docfreq = 2)
```

Finally, `keyATM_read` function reads your data for **keyATM**.

```{r, warning=FALSE, message=FALSE}
keyATM_docs <- keyATM_read(texts = data_dfm)
summary(keyATM_docs)
```

Researchers are required to remove any documents 
that do not contain any terms
before using the `keyATM_read()` function.
If there are documents that do not contain any terms, 
the `keyATM_read()` function raises a warning.
It is highly recommended to manually check documents with length 0
before fitting the model, otherwise, the **keyATM** will
automatically drop these documents when fitting a model.
Even so, we suggest users to remove documents that do not contain
any words as a part of preprocessing. As explained in the later section, 
this process is especially 
critical when the covariate model or the dynamic model is fitted. 
The example below shows the warning that the
`keyATM_read()` function displays.


```{r, include=FALSE, warning=FALSE, message=FALSE, fig.align='center'}
data_dfm_len0 <- data_dfm
data_dfm_len0[10, ] <- rep(0, ncol(data_dfm_len0))
data_dfm_len0[50, ] <- rep(0, ncol(data_dfm_len0))
class(data_dfm_len0) <- c("dfm")
```

```{r, warning=TRUE, message=FALSE, fig.align='center'}
keyATM_docs0 <- keyATM_read(texts = data_dfm_len0)
```

The warning message above indicates that there are two documents 
in `data_dfm_len0` that do not contain any terms (the index 10 and 50). 
In the **quanteda**, we can easily remove documents 
without any word counts with the following function.

```{r, eval=FALSE, warning=FALSE, message=FALSE, fig.align='center'}
data_dfm_rm0 <- dfm_subset(data_dfm_len0, ntoken(data_dfm_len0) > 0)
```

### Alternative ways to load texts into **keyATM**
There are two other ways to read texts, which we do not recommend. 
Please make sure to preprocess texts with other packages or softwares. 
In both methods, each word should be separated by a single space. 

#### Using data.frame or tibble:
`keyATM_read()` can read `data.frame` and `tibble` if you preprocess texts without **quanteda**. 
Please store texts in a column named `text`.
Below shows the example of the required data format.

```
> head(docs)  # `docs` stores preprocessed texts
# A tibble: 6 x 1
  text                                                                      
  <chr>                                                                     
1 h.r h.r one hundred first congress congress congress united u...
2 first congress one congress congress united united state stae...
3 one one one one one one one one one one one one one one one o...
4 h.r h.r one one one hundred hundred first first congress cong...
5 congress congress one united united united united united unit...
6 h.r h.r one one one one one hundred hundred first congress co...
```

```{r, eval=FALSE, warning=FALSE, message=FALSE}
# Read texts into keyATM
keyATM_docs <- keyATM_read(docs)
```

#### Reading directly from files:
If you have preprocessed text files, you can pass a list of files to `keyATM_read()`.
```{r, eval=F, warning=FALSE, message=FALSE, fig.align='center'}
# Create a list of paths to text files
textfiles <- list.files(PATH_TO_THE_FOLDER, pattern = "*.txt", full.names = TRUE)

# Read texts into keyATM
keyATM_docs <- keyATM_read(textfiles)
```

## Preparing keywords
### Create keywords list
Feeding keywords into models plays an essential role in the **keyATM**. 
Researchers are expected to use their substantive knowledge and
to carefully select keywords.

In this application, suppose we are interested in five topics, 
*Government*, *Congress*, *Peace*, *Constitution*, and *Foreign affairs*
and choose keywords for each of these topics.
```{r, warning=FALSE, message=FALSE, fig.align='center'}
keywords <- list(Government     = c("laws", "law", "executive"),
                 Congress       = c("congress", "party"),
                 Peace          = c("peace", "world", "freedom"),
                 Constitution   = c("constitution", "rights"),
                 ForeignAffairs = c("foreign", "war"))
```

A set of keywords should be stored in a list object, and we recommend users to name each topic for clarity.
Each keyword-topic can have a different number of keywords.

### Checking keywords
Keywords should appear reasonable times (typically more than 0.1% of the corpus) in the documents.
The `visualize_keywords()` function plots the frequency of keywords by topic.

```{r, warning=FALSE, message=FALSE, fig.align='center', height=3, width=3}
key_viz <- visualize_keywords(docs = keyATM_docs, keywords = keywords)
key_viz
```
The figure helps you to check the frequency of keywords. Including low-frequency keywords do not help the model in general. 

Proportion is defined as a number of times a keyword occurs in the corpus divided by the total length of documents. This measures the frequency of the keyword in the corpus. Formally, the proportion of the keyword $v$ is,
$$
\begin{align*}
    \text{Proportion of }v = \frac{\sum_{d=1}^{D} \sum_{i=1}^{N_d} I(w_{di} = v) }{\sum_{d=1}^{D} N_d}
\end{align*}
$$
where $N_d$ is the length of the document $d$ and $I$ is an indicator function. Keywords of each topic are ordered by the proportion (x-axis).

You can save the plot with the `save_fig()` function,
```{r, eval=FALSE, warning=FALSE, message=FALSE, fig.align='center', height=3, width=3}
key_viz <- visualize_keywords(docs = keyATM_docs, keywords = keywords)
save_fig(key_viz, "figures/keyword.pdf", width = 6.5, height = 4)
```

and get the actual values with the `values_fig()` function.

```{r, warning=FALSE, message=FALSE, fig.align='center'}
values_fig(key_viz) 
```

The `prune` argument of the `visualize_keywords()` function is `TRUE` by default. 
It drops keywords that do not appear in the corpus 
and raises a warning if there is any.
```{r, warning=TRUE, message=FALSE}
keywords_2 <- list(Government = c("laws", "law", "non-exist"))
key_viz2 <- visualize_keywords(docs = keyATM_docs, keywords = keywords_2)
```

If all keywords assigned to a topic is pruned, it raises an error.
```{r, warning=FALSE, error = TRUE, message=FALSE}
keywords_3 <- list(Government = c("non-exist", "non-exist2"))
key_viz3 <- visualize_keywords(docs = keyATM_docs, keywords = keywords_3)
```

## Next Step
Now you have texts and keywords! The next step is to fit a model with the `keyATM()` function. **keyATM** has three models:

* [keyATM Base](keyATM_base.html)
  * This is an extension of the most famous topic model, Latent Dirichlet Allocation.
  * If you do not have covariates, this model is your first option.
* [keyATM Covariates](keyATM_cov.html)
  * If you have covariates, please use this model.
  * This model uses document-level meta data (document-level covariates) to model topic prevalence (the prior of document-topic distribution).
* [keyATM Dynamic](keyATM_dynamic.html)
  * If you want to explicitly consider time structure, please use this model.


You can find details in [FAQ](FAQ.html#which-model-to-use).
