---
title: "Preparation"
output: 
  html_document:
    toc: false
---


## Prepare Texts
To fit topic models with **keyATM**, uesrs need to prepare texts for `keyATM_read()`. `keyATM_read()` has three ways to input texts.

### Use quanteda dfm (recommended)

**keyATM** can read a `dfm` object created by **quanteda** package. Since **keyATM** does not provide preprocessing functions, we recommend users to preprocess documents with **quanteda**. Please visit [quanteda Quick Start: Creating a Corpus](https://quanteda.io/articles/quickstart.html#creating-a-corpus) to see how to create a `corpus` object.

By making a `token` object from a `corpus` object, **quanteda** can perform various preprocessing methods ([quanteda Quick Start: Tokenizing texts](https://quanteda.io/articles/quickstart.html#tokenizing-texts)).

Lastly, you can make a `dfm` object with a function `dfm()` in **quanteda**.


### Use data.frame or tibble
`keyATM_read()` can read `data.frame` and `tibble` if you preprocess texts without **quanteda**. Please store texts in a column named `text`.

```
> head(docs)  # `doc` stores preprocessed texts
# A tibble: 6 x 1
  text                                                                      
  <chr>                                                                     
1 h.r h.r one hundred first congress congress congress united u...
2 first congress one congress congress united united state stae...
3 one one one one one one one one one one one one one one one o...
4 h.r h.r one one one hundred hundred first first congress cong...
5 congress congress one united united united united united unit...
6 h.r h.r one one one one one hundred hundred first congress co...
```

### Read directly from files
If you have preprocessed text files, you can pass a list of files to `keyATM_read()`.

```{r, eval=F, warning=FALSE, message=FALSE, fig.align='center'}
textfiles <- list.files(PATH_TO_THE_FOLDER, pattern = "*.txt", full.names = TRUE)
```

## Prepare keywords

Keywords should be in a list. For example, let's prepare two keyword-topics. The number of keywords can vary between topics. Please also check [FAQ](FAQ.html) to see how to select keywords that help models.

```{r, eval=F, warning=FALSE, message=FALSE, fig.align='center'}
keywords_list <- list(
                      c("election", "vote", "voter"),
                      c("economy", "recession")
                     )
```


## Next Step
Now you have texts and keywords! The next step is to prepare a model object with `keyATM_read()`. **keyATM** has three models:

* [keyATM Basic](keyATM_basic.html)
  * This is an extension of the most famous topic model, Latent Dirichlet Allocation.
  * If you do not have covariates, this model is your first option.
* [keyATM Covariate](keyATM_cov.html)
  * If you have covariates, please use this model.
  * This model uses covariates to model topic prevalence (the prior of document-topic distribution).
* [keyATM HMM](keyATM_HMM.html)
  * If you want to explicitly consider time structure, please use this model.


You can find details in [FAQ](FAQ.html#which-model-to-use).


