---
title: "Preparation"
output: 
  html_document:
    toc: false
---


## Preparing Texts
To fit topic models with **keyATM**, uesrs need to prepare texts for `keyATM_read()`. `keyATM_read()` has three ways to input texts.

### Using quanteda dfm (recommended)

**keyATM** can read a `dfm` object created by **quanteda** package. Since **keyATM** does not provide preprocessing functions, we recommend users to preprocess documents with **quanteda**. Please visit [quanteda Quick Start: Creating a Corpus](https://quanteda.io/articles/quickstart.html#creating-a-corpus) to see how to create a `corpus` object.

By making a `token` object from a `corpus` object, **quanteda** can perform various preprocessing methods ([quanteda Quick Start: Tokenizing texts](https://quanteda.io/articles/quickstart.html#tokenizing-texts)).

Lastly, you can make a `dfm` object with a function `dfm()` in **quanteda**.

Here is an example preprocessing steps with **quanteda**. In this example, we read texts with **readtext** package.
```{r, eval=F, warning=FALSE, message=FALSE, fig.align='center'}
library(quanteda)
library(readtext)

raw_docs <- readtext("PATH_TO_THE_FOLDER/*.txt",
                     encoding = "UTF-8")

key_corpus <- corpus(raw_docs, text_field = "text")

key_tokens <- tokens(key_corpus,
                     remove_numbers = TRUE, 
                     remove_punct = TRUE, 
                     remove_symbols = TRUE,
                     remove_separators = TRUE,
                     remove_url = TRUE) %>%
                tokens_tolower() %>%
                tokens_remove(stopwords("english")) %>%
                tokens_select(min_nchar = 3)

key_dfm <- dfm(key_tokens) %>%
             dfm_trim(min_termfreq = 5, min_docfreq = 2)
```

You can also use `c(stopwords("english"), "your", "stopwords")` if you want to add corpus specific stopwords.


### Using data.frame or tibble
`keyATM_read()` can read `data.frame` and `tibble` if you preprocess texts without **quanteda**. Please store texts in a column named `text`.

```
> head(docs)  # `docs` stores preprocessed texts
# A tibble: 6 x 1
  text                                                                      
  <chr>                                                                     
1 h.r h.r one hundred first congress congress congress united u...
2 first congress one congress congress united united state stae...
3 one one one one one one one one one one one one one one one o...
4 h.r h.r one one one hundred hundred first first congress cong...
5 congress congress one united united united united united unit...
6 h.r h.r one one one one one hundred hundred first congress co...
```

### Reading directly from files
If you have preprocessed text files, you can pass a list of files to `keyATM_read()`.

```{r, eval=F, warning=FALSE, message=FALSE, fig.align='center'}
textfiles <- list.files(PATH_TO_THE_FOLDER, pattern = "*.txt", full.names = TRUE)
```

## Reading documents into keyATM
```{r, include = F, warning=FALSE, message=FALSE, fig.align='center'}

```

Before fitting the model, we need to read texts and keywords into **keyATM**. Here we use **quanteda**'s `dfm`.

**keyATM** package includes a tidy dataset for illustration purpose. In this example, we use ***. You can load this data by `data(keyATM_data_bills)`.
```{r, warning=FALSE, message=FALSE, fig.align='center'}
library(quanteda)
library(keyATM)
data(keyATM_data_bills)
bills_dfm <- keyATM_data_bills$doc_dfm  # quanteda object
keyATM_docs <- keyATM_read(bills_dfm)
```

## Preparing keywords

### Keywords list
Keywords should be in a list. For example, we prepare four keyword-topics. Keywrods should be stored in a list. Each element in the list is a character vector, which corresponds to a single keyword-topic. The number of keywords can vary between topics. 

```{r, warning=FALSE, message=FALSE, fig.align='center'}
bills_keywords <- list(
                       Education = c("education", "child", "student"),
                       Law       = c("court", "law", "attorney"),
                       Health    = c("public", "health", "program"),
                       Drug      = c("drug", "treatment")
                      )
```


### Checking keywords
```{r, warning=FALSE, message=FALSE, fig.align='center', height=3, width=3}
visualize_keywords(keyATM_docs, bills_keywords)
```
The figure helps you to check the frequency of keywords. Including low-frequency keywords do not help the model in general. **keyATM** automatically prune keywords that do not appear in the documents.


## Next Step
Now you have texts and keywords! The next step is to prepare a model object with `keyATM_read()`. **keyATM** has three models:

* [keyATM Base](keyATM_base.html)
  * This is an extension of the most famous topic model, Latent Dirichlet Allocation.
  * If you do not have covariates, this model is your first option.
* [keyATM Covariates](keyATM_cov.html)
  * If you have covariates, please use this model.
  * This model uses covariates to model topic prevalence (the prior of document-topic distribution).
* [keyATM Dynamic](keyATM_dynamic.html)
  * If you want to explicitly consider time structure, please use this model.


You can find details in [FAQ](FAQ.html#which-model-to-use).


