---
title: "Weighted LDA Models"
output: 
  html_document:
    toc: true
---

```{r setup II, include=FALSE, eval=TRUE}
knitr::opts_chunk$set(eval = T, echo = TRUE)
```

## Weighted LDA
We use the text data we prepared for the base keyATM (see [Preparation](Preparation.html#preprocessing-data)).
```{r,  warning=FALSE, message=FALSE, fig.align='center'}
library(keyATM)
library(quanteda)
library(magrittr)
data(data_corpus_inaugural, package = "quanteda")

data_tokens <- tokens(data_corpus_inaugural,
                      remove_numbers = TRUE, 
                      remove_punct = TRUE, 
                      remove_symbols = TRUE,
                      remove_separators = TRUE,
                      remove_url = TRUE) %>%
                 tokens_tolower() %>%
                 tokens_remove(c(stopwords("english"), 
                               "may", "shall", "can",
                               "must", "upon", "with", "without")) %>%
                 tokens_select(min_nchar = 3)

data_dfm <- dfm(data_tokens) %>%
              dfm_trim(min_termfreq = 5, min_docfreq = 2)

keyATM_docs <- keyATM_read(texts = data_dfm)
```

```{r, warning=FALSE, message=FALSE, fig.align='center', results="hide"}
out <- weightedLDA(docs              = keyATM_docs,    # text input
                   number_of_topics  = 5,              # number of topics without keywords
                   model             = "base",         # select the model
                   options           = list(seed = 250))
```
```{r, warning=FALSE, message=FALSE}
top_words(out)
```

## Weighted LDA Covariates
We use the covariate data we prepared for the covariate keyATM (see [keyATM_cov](keyATM_cov.html#preparing-covariates)).
```{r,  warning=FALSE, message=FALSE, fig.align='center'}
vars <- docvars(data_corpus_inaugural)

library(dplyr)
vars %>%
  as_tibble() %>%
  mutate(Period = case_when(Year <= 1899 ~ "18_19c",
                            TRUE ~ "20_21c")) %>%
  mutate(Party = case_when(Party == "Democratic" ~ "Democratic",
                           Party == "Republican" ~ "Republican",
                           TRUE ~ "Other")) %>%
  select(Party, Period) -> vars_selected

vars_selected %>%
  mutate(Party  = factor(Party, 
                         levels = c("Other", "Republican", "Democratic")),
         Period = factor(Period, 
                         levels = c("18_19c", "20_21c"))) -> vars_selected
```

```{r, warning=FALSE, message=FALSE, fig.align='center', results="hide"}
out <- weightedLDA(docs              = keyATM_docs,
                   number_of_topics  = 5,
                   model             = "covariates",
                   model_settings    = list(covariates_data    = vars_selected, 
                                            covariates_formula = ~ Party + Period),
                   options           = list(seed = 250))
```
```{r, warning=FALSE, message=FALSE}
top_words(out)
```


## Weighted LDA Dynamic
We use the time index we prepared for the dynamic keyATM (see [keyATM_dynamic](keyATM_dynamic.html#preparing-time-index)).
```{r, warning=FALSE, message=FALSE, fig.align='center'}
vars %>%
  as_tibble() %>%
  mutate(Period = (vars$Year - 1780) %/% 10 + 1) -> vars_period
```


```{r, warning=FALSE, message=FALSE, fig.align='center', results="hide"}
out <- weightedLDA(docs             = keyATM_docs,  
                   number_of_topics = 3,            
                   model            = "dynamic",    
                   model_settings   = list(time_index = vars_period$Period, 
                                           num_states = 5),
                   options          = list(seed = 250))

```

```{r, warning=FALSE, message=FALSE}
top_words(out)
```



